Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
reformat replies

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\todoKC{rewrite this abstract based on the comparision table. -Jeremy}
  Gradual Typing is great. Implementing gradually typed with blame
  tracking and space efficiency is tricky. There exist two technique
  to do this: coercion and threesome. Coercion is easy to understand,
  and easy enough to implement, but difficult to reason about
  formally. Threesome is hard to understand, easy to implement, and
  easy to reason about formally. We propose hypercoercion, which is
  easy to understand, as easy to implement as coercion, and easy to
  reason about formally.
\end{abstract}

@@

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -Jeremy}
\todo[inline]{Will fix grammar after fixing all other problems -KC}
\todo[inline]{The first paragraph of the introduction should summarize
  the entire introduction, and in some sense, the entire paper. -Jeremy}

@@

\citet{siek2009exploring} present another intermediate langauge for gradually 
typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
and space-efficiency for this language by decorating \citet{herman2010space}'s 
coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
with the dynamic type and cast expressions. The labels in \castCalculus\, 
unlike their counterparts in the Blame Calculus, have no polarity. 
They also propose that there are four blame strategies for \castCalculus{}:
$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
differently. They claim that their \lazyUD\ cast calculus is the same as the 
Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
however, whether the simulation in the other direction also works.
\todo[inline]{Is it important to this paper whether there is a
  simulation in the other direction? -Jeremy}
\todo[inline]{I guessed to say coercion is correct the other direction is 
necessary. -KC}

@@

Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown an function that 
composes and produces normal coercions.
%
\todo[inline]{Many researchers would view this as a positive thing,
  not a negative. For example, the notion of normal forms comes up
  over and over again in mathematics and logic. -Jeremy}
\todo[inline]{I guess having a notion of normal forms is more convenient when a 
notion of normalization is convenient. But we don't even need a notion of 
normalization for cast representations. -KC}

@@

We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
We care more about lazy strategies because recently, \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that these strategies are not very ideal. 
\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy}
\todo[inline]{Explained, not sure if it suffice. -KC}

The structure of this paper is as follows. 
Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ Blame 
Calculi. 
Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ Coercion 
Calculi. 
In section \ref{sec:hypercoercion} we present hypercoercion.
Section \ref{sec:conclude} concludes.
\todo[inline]{Lots of missing sections. -Jeremy}
\todo[inline]{Will fix finally, I am moving stuff. -KC}

@@

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
types and product types, and annotates function codomain explicitly. 
Its semantics depend on blame strategies, so we defer them to sub-sections.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy}
\todoKCFixed{}
\todo[inline]{The term typing rule for casts is broken. -Jeremy}
\todoKCFixed{}

@@

Let $ e $ range over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
\todo[inline]{Why do you annotate the codomain of lambda abstractions
  explicitly? -Jeremy}
\todo[inline]{Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines \citep{felleisen1986control}.
\todo[inline]{Briefly present the main ideas regarding how a CEK
  machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Use citep to put a citation in parentheses, as I've
  done above. -Jeremy }
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy}
We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

@@

\todo[inline]{Give a summary statement about the shape of the normal form.}
\todo[inline]{The three-part shape is not obvious before the transformation at 
the end of the next paragraph. So the summary is given after that. -KC}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\todoKC{rewrite this abstract based on the comparision table.}
  Gradual Typing is great. Implementing gradually typed with blame
  tracking and space efficiency is tricky. There exist two technique
  to do this: coercion and threesome. Coercion is easy to understand,
  and easy enough to implement, but difficult to reason about
  formally. Threesome is hard to understand, easy to implement, and
  easy to reason about formally. We propose hypercoercion, which is
  easy to understand, as easy to implement as coercion, and easy to
  reason about formally.
\end{abstract}

@@

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -Jeremy
  \\---\\
  Will fix grammar after fixing all other problems -KC}
\todo[inline]{The first paragraph of the introduction should summarize
  the entire introduction, and in some sense, the entire paper. -Jeremy}

@@

\citet{siek2009exploring} present another intermediate langauge for gradually 
typed language, cast calculus \castCalculus\ and achieve both blame-tracking 
and space-efficiency for this language by decorating \citet{herman2010space}'s 
coercions with labels. \castCalculus\ is simply typed lambda calculus extended 
with the dynamic type and cast expressions. The labels in \castCalculus\, 
unlike their counterparts in the Blame Calculus, have no polarity. 
They also propose that there are four blame strategies for \castCalculus{}:
$ \{Lazy, Eager\} \times \{D, UD\} $. Eager strategies detect more potential 
type errors, but blame more programs. $ D $ and $ UD $ assign blame labels 
differently. They claim that their \lazyUD\ cast calculus is the same as the 
Blame Calculus, modulo label polarity, and prove that their their \lazyUD\ 
coercion calculus simulates their \lazyUD{} cast calculus. It is unknown, 
however, whether the simulation in the other direction also works.
\todo[inline]{Is it important to this paper whether there is a
simulation in the other direction? -Jeremy
\\ --- \\
I guessed to say coercion is correct the other direction is 
necessary. -KC}

@@

Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown an function that 
composes and produces normal coercions.
%
\todo[inline]{Many researchers would view this as a positive thing,
  not a negative. For example, the notion of normal forms comes up
  over and over again in mathematics and logic. -Jeremy
\\ --- \\
I guess having a notion of normal forms is more convenient when a 
notion of normalization is convenient. But we don't even need a notion of 
normalization for cast representations. -KC}

@@

We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
We care more about lazy strategies because recently, \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that these strategies are not very ideal. 
\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy
	\\ --- \\ Explained, not sure if it suffice. -KC}

The structure of this paper is as follows. 
Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ Blame 
Calculi. 
Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ Coercion 
Calculi. 
In section \ref{sec:hypercoercion} we present hypercoercion.
Section \ref{sec:conclude} concludes.
\todo[inline]{Lots of missing sections. -Jeremy}

@@

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
types and product types, and annotates function codomain explicitly. 
Its semantics depend on blame strategies, so we defer them to sub-sections.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy
\\ --- \\ Fixed -KC}

@@

Let $ e $ range over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
\todo[inline]{Why do you annotate the codomain of lambda abstractions
  explicitly? -Jeremy
  \\---\\
  Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines \citep{felleisen1986control}.
\todo[inline]{Briefly present the main ideas regarding how a CEK
  machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Use citep to put a citation in parentheses, as I've
  done above. -Jeremy }
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy
\\---\\
Could you tell me why taking the value first is better?
I am always taking the target of induction/match first. -KC}
We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

@@

\todo[inline]{Give a summary statement about the shape of the normal form. 
-Jeremy
\\---\\The three-part shape is not obvious before the transformation at 
the end of the next paragraph. So the summary is given after that. -KC}
